Enhancement of SDR in Thessaloniki

### 2024-09-07 GHI_enh_08_validation.tex
Commit 2024-09-07 09:10

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-06}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Drop all enhacement cases
\end{verbatim}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-6-1}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-6}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-1}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-7-1}
\end{figure}

@@

\begin{verbatim}
Loading required package: ggpp
\end{verbatim}

\begin{verbatim}
Registered S3 methods overwritten by 'ggpp':
  method                  from   
  heightDetails.titleGrob ggplot2
  widthDetails.titleGrob  ggplot2
\end{verbatim}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-2}

\caption{ - empty caption - }\label{fig:unnamed-chunk-7-2}
\end{figure}

@@

\begin{verbatim}
2024-09-06 19:52:22.8 athan@tyler GHI_enh_08_validation.R 21.715553 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-07}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Registered S3 methods overwritten by 'ggpp':
  method                  from   
  heightDetails.titleGrob ggplot2
  widthDetails.titleGrob  ggplot2
\end{verbatim}

\begin{verbatim}
Drop all enhacement cases
\end{verbatim}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/P-validation-cloudfree-GHI-1}

@@

\caption{ - empty caption - }\label{fig:P-validation-cloudfree-GHI}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/P-validation-threshold-GHI-1}

@@

\caption{ - empty caption - }\label{fig:P-validation-threshold-GHI}
\end{figure}

@@

@@

\begin{verbatim}
2024-09-07 05:12:02.5 athan@tyler GHI_enh_08_validation.R 5.397558 mins
\end{verbatim}
